---
title: "Get a entire summary statistic"
author: "Oscar Ramirez Alan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
self_contained: no
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-")
```

```{r, echo = FALSE}
"R CMD build --no-build-vignettes pkgname" 
```

# resumeRdesc

The goal of resumeRdesc is to get a entire summary statistic.

You have installed resumeRdesc on your R system, version 3.4.4 or later “https://cran.r-project.org/”. Works better in Rstudio “https://www.rstudio.com”


## Installation

You can install the released version of resumeRdesc from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("resumeRdesc"). Not yet available
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("osoramirez/resumeRdesc")
```
## Example

Activate the resumeRdesc package:

```{r}
library(resumeRdesc)
```

You could requiere “e1071”; “car” and “carData” package


This is a basic example which shows you how to solve a common problem:

```{r example, fig.width=7, fig.height=5}
set.seed(12345)
data<-rnorm(100)
resume(rnorm(100))
```

Get a complete summary table, histogram and boxplot of your distribution data.

```{r resume,fig.width=7, fig.height=5}
resume2data(data)
```

If you are interested in exploring the distribution of your data using a histogram, use “plothist”.



```{r histogram, echo = FALSE , fig.width=7, fig.height=5}
plothist(data)
```

You can also embed boxplot, for example:


```{r fig.width=7, fig.height=5}
plotbox(data)
```


##Coefficient of variation

A coefficient of variation (cv) is a statistical measure of the dispersion of data points in a data series around the mean.

```{r}
cv(data)
```


##Geometric mean

The geometric mean is a mean or average, which indicates the central tendency

```{r}
g_mean(data)
```


##Harmonic mean

The harmonic mean is a very specific type of average. It’s generally used when dealing with averages of units, like speed or other rates and ratios. Its a reciprocals of the numbers in your data set or it is calculated by dividing the number of observations by the reciprocal of each number in the series.

```{r}
h_mean(data)
```


##Mode

The "Mode" is the value that occurs most often. If no number in the list is repeated.

```{r}
data2<-c(1,1,1,2,3,4,5,6,7,8,9)
Mode(data2)
```


##Standard error

Is as a measure of the precision of the sample mean, it is  considered as a measures of spread.

```{r}
se(data)
```


##Kurtosis

Kurtosis is a measure of whether the data are heavy-tailed or light-tailed relative to a normal distribution.

```{r}
K(data)
```

#Skewness 

Skewness is a measure of symmetry, or the lack of symmetry. 

```{r}
skew(data)
```



#summaries for data.frame
For your data.frame data use this functions.

```{r fig.width=7, fig.height=5}
data(iris)
resumendf(Petal.Width ~Species, data = iris)
```

#Reference

Read more: Harmonic Mean https://www.investopedia.com/terms/h/harmonicaverage.asp#ixzz5Ibmy4Rbq 


Read more: Coefficient Of Variation (CV) https://www.investopedia.com/terms/c/coefficientofvariation.asp#ixzz5Ibl3v4Ly 

Read more: Standard error
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1255808/
